Towards Transparency and Open Science

### 2023-01-12 manuscript.Rmd
adjust spacing for abstract

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
header-includes: |
  \usepackage{libertine}
  \usepackage{pdfpages}
  \usepackage{titling}
  \pretitle{\begin{center}\LARGE
     \begin{minipage}{\textwidth}
     \includepdf{cover.pdf}
     \end{minipage}
     \newpage}
  \posttitle{\end{center}}
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 12pt
linestretch: 1.2
geometry: "left=3.6cm, right=3.6cm, top=4cm, bottom=4cm, bindingoffset=5mm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---

>>>>

---
title: "Towards Transparency and Open Science"
subtitle: "A Principled Perspective on Computational Reproducibility and Preregistration"
output:
  bookdown::pdf_document2:
    latex_engine: "xelatex"
    toc: true
    number_sections: false
header-includes: |
  \usepackage{libertine}
  \usepackage{pdfpages}
  \usepackage{titling}
  \pretitle{\begin{center}\LARGE
     \begin{minipage}{\textwidth}
     \includepdf{cover.pdf}
     \end{minipage}
     \newpage}
  \posttitle{\end{center}}
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
  \setotherlanguage[]{german}
fontsize: 12pt
linestretch: 1.2
geometry: "left=3.6cm, right=3.6cm, top=4cm, bottom=4cm, bindingoffset=5mm"
papersize: a4
bibliography: references.bib
abstract: "`r paste0(c('\\\\setstretch{1.0}English:', readLines('abstract.md'), '\\\\par Deutsch:\\\\textgerman{', readLines('zusammenfassung.md'), '}\\\\newpage'), collapse = ' ')`"
csl: apa.csl
repro:
  files:
    - abstract.md
    - apa.csl
    - papers/
  tlmgr:
    - pgf
    - preview
    - libertine
    - pdfpages
  apt:
    - git
    - rsync
---
